Informing policy via dynamic models: Cholera in Haiti

### 2023-06-30 ms.Rnw
minor edit

# haiti3_fit contains ll estimate for many parameter sets, so we want to find
# the highest value
mod3_ll <- max(
  haiti3_fit[[length(haiti3_fit)]]$logLiks[, 'logLik'],
  na.rm = TRUE
)

>>>>

# haiti3_fit contains ll estimate for many parameter sets, so we want to find
# the highest value
mod3_ll <- max(
  haiti3_fit[[length(haiti3_fit)]]$logLiks$logLik,
  na.rm = TRUE
)
